\chapter{Related Work}

	In order to learn the current state-of-the-art methods of auto-generating business process models and thus answer the research question comprehensively, a systematic literature review must be performed so that we can learn what kind of efforts are made as well as what are the most preferred techniques and what open challenges exist. The literature review is conducted under the guidance of Kitchenham et al. given in their paper \cite{literature_review_guidance}. The work consists of several stages: Firstly, the electronic database used to run the search is chosen. Then the selection criteria are defined, and articles are filtered accordingly. After that, a horizontal search will be run to cover as many papers as possible. Finally, a list of the final literature is studied carefully, and helpful information is extracted.

	\begin{table}[]
		\centering
		\caption{\centering Overview of Systematic Literature Review Protocol}
		\begin{tabular}{lccl}
    	\textbf{Database}\hspace{30mm} & \textbf{hits} & \textbf{selected} &  \\
    	\hline
		IEEE                     		& 56   & 5   &      		\\
		Springer                 		& 275  & 8   &      		\\
		ACM                      		& 201  & 2   &      		\\
		Google scholar           		& 31   & 3   &      		\\
		\hline
		Result horizontal search	 	& 563  & 18  &      		\\
		Vertical search          		&      & 2   &  \hspace{5mm}add papers  \\
		\hline
		Overall                  		&      & 20   &     
		\end{tabular}
	\end{table}
	
% search string
	To perform a comprehensive literature review, we chose three most famous electronic databases, i.e., IEEE, Springer, and ACM. Nevertheless, only using these three databases, There is still a minor chance that some important articles will be missed. Therefore, we also used Google scholar as a complement because it covers a wide range of literature, from conference papers to degree theses. The search string used for the literature review is developed using two keywords, which are the most important ones for our research: \textit{business process model} and \textit{natural language processing}.
	
% selection criteria
	In the next step, inclusion and exclusion criteria should be defined. They describe a list of desired and undesired features for the literature selection to obtain relevant studies and support our research and future work. Inclusion criteria were developed as follows: \textbf{IC-1}: NLP should have high relevance to the research paper. \textbf{IC-2}: BPMN should have high relevance to the research paper. \textbf{IC-3}: The research paper should describe the generation of the BPMN model using NLP. Exclusion criteria were: \textbf {EC-1}: the research paper is not written in English. \textbf{EC-2}: The research paper is not in the form of a proper scientific article. 
	
	During the literature selection, the first step was to identify duplicates since multiple electronic databases were used. Duplicates refer to articles that have the same title and authors. In the next step, we read the article's title, abstract and introduction parts and applied the inclusion and exclusion criteria to shape the final result further. Finally, we read the whole article and then performed a vertical search to identify the related papers used in our selected papers. As a final result, 17 papers were chosen. Among the chosen papers, \cite{literature_review_1} \cite{literature_review_2} \cite{literature_review_3} \cite{literature_review_4} are literature reviews that analyzed the development and usage of process model generation methods. \cite{literature_review_3} points out that the NLP is the most widely adopted method and it can also be combined with other methods to increase accuracy. \cite{literature_review_1} and \cite{literature_review_3} give a list of tools for NLP and process model generation that have been used in previous works. \cite{literature_review_4} compares several papers using NLP to extract process models with different inputs and concludes the typical steps that have to be performed. \cite{complement_2} and \cite{complement_3} propose their findings in identifying the inconsistencies between the textual description and the generated process model. 
	
%todo: vertical好了以后把这个几篇文章补上
	
	A novel breakthrough is made in the work of \cite{t2m_1}, where they developed a method which extracts information from textual descriptions to automatically generate the business process models regardless of the structure of the input text. The Authors performed three vital steps to process the text input: (i) the syntax parsing using the Stanford Parser, (ii) semantic analysis using FrameNet and WordNet, and (iii) anaphora resolution. Finally, they can generate a process model based on the data. Some limitations of this work are addressed in \cite{pre_processing_1}: The textual description must be grammatically correct, otherwise the model will produce an incorrect output. Furthermore, the process in the description must develop sequentially and cannot contain examples or questions. Another work offered in \cite{t2m_2} focuses on the extraction of declarative process models to address the problem that many NLP models can only handle the imperative process models. This is done by introducing many grammatical constraints to analyze the relationship of words. Among all works, with little focus on the visualization of the process model, \cite{complement_1} introduces a web-based NLP model extraction service. However, this work leverages the extraction model of others, and thus the output accuracy cannot be well guaranteed. A possible research gap is to leverage the findings in \cite{pre_processing_1} and \cite{t2m_2} to overcome the weakness of the model in \cite{t2m_1}. Moreover, \cite{complement_1} provides a good idea of visualization, where a front-end interface is implemented.
	
	
	
	
	
	
	